Type-Safe Modular Parsing

### 2016-12-22 paper/sections/ParsingLibrary.tex
Comments on Sec 6

@@

@@

Having pointed out that our goal is to realize modular and extensible parsers, we recommend users to write code in a modular and
organized way. The framework we use for a language, or rather a language component in our case study, consists of the following three
parts:
\begin{itemize}
\item \textbf{Object Algebra interface:} defined as a trait for the abstract syntax, with several methods corresponding to the production rules.
\item \textbf{Parser:} implementation of the parser with lexing, using open recursion and Object Algebras, with its scoping trait abstracted over the type parameters.
\item \textbf{Algebra (optional):} some behaviors (operations) on the data structure, such as pretty-printing and so on.
\end{itemize}

@@

>>>>

\huang{These alternatives could be discussed in the discussion section, not here. 6.1 could only talks about library code. And the titles should be changed as well}

@@

\huang{code needs to be polished}

@@

\huang{The point of introducing Language Component could be: modular parsers enable us to build modular language features. We can abstract language features, compose them and thus reuse them. A language feature covers all the related stuffs we need, as a combination of syntax+parsing+operations. Rather than: we recommend users to ...}

Having pointed out that our goal is to realize modular and extensible parsers, we recommend users to write code in a modular and
organized way. The framework we use for a language, or rather a language component in our case study, consists of the following three
parts:
\begin{itemize}
    \item \textbf{Object Algebra interface:} defined as a trait for the abstract syntax, with several methods corresponding to the production rules. \huang{Production rule is about the \emph{concrete} syntax, The methods correspond to \emph{abstract} syntax. }
\item \textbf{Parser:} implementation of the parser with lexing, using open recursion and Object Algebras, with its scoping trait abstracted over the type parameters.
\item \textbf{Algebra (optional):} some behaviors (operations) on the data structure, such as pretty-printing and so on.
\end{itemize}

@@

\huang{the title could be more concrete, as all of the content is about the usage of langauge components}

\huang{need to refactor the code as well}
